% Autogenerated translation of _index.md by Texpad
% To stop this file being overwritten during the typeset process, please move or remove this header

\documentclass[12pt]{book}
\usepackage{graphicx}
\usepackage{fontspec}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,left=.5in,right=.5in,top=.3in,bottom=0.3in]{geometry}
\setlength\parindent{0pt}
\setlength{\parskip}{\baselineskip}
\setmainfont{Helvetica Neue}
\usepackage{hyperref}
\pagestyle{plain}
\begin{document}

\hrule
\chapter*{Display name}

title: Béla Figge

\chapter*{Is this the primary user of the site?}

superuser: true

\chapter*{Role/position/tagline}

role: Ph.D. in Economics

\chapter*{Organizations/Affiliations to show in About widget}

organizations:
- name: Georgia State University
  url: https://aysps.gsu.edu

\chapter*{Short bio (displayed in user profile at end of posts)}

\chapter*{Interests to show in About widget}

interests:
- Applied Microeconomics
- Causal Inference

\chapter*{Education to show in About widget}

education:
  courses:
  - course: Ph.D. in Economics
    institution: Georgia State University
    year: 2022 

\chapter*{Social/Academic Networking}

\chapter*{For available icons, see: https://wowchemy.com/docs/getting-started/page-builder/\#icons}

\chapter*{For an email link, use "fas" icon pack, "envelope" icon, and a link in the}

\chapter*{form "mailto:your-email@example.com" or "/\#contact" for contact widget.}

social:
- icon: envelope
  icon\emph{pack: fas
  link: '/\#contact'
- icon: twitter
  icon}pack: ai
  link: https://twitter.com/BelaFigge
- icon: graduation-cap  \# Alternatively, use \texttt{google-scholar} icon from \texttt{ai} icon pack
  icon\emph{pack: fas
  link: https://scholar.google.com/citations?user=KmpVxdUAAAAJ\&hl=en
- icon: github
  icon}pack: fab
  link: https://github.com/bfigge
- icon: linkedin
  icon\_pack: fab
  link: https://www.linkedin.com/in/bela-figge/

\chapter*{Link to a PDF of your resume/CV.}

\chapter*{To use: copy your resume to \texttt{static/uploads/bfigge\_cv.pdf}, enable \texttt{ai} icons in \texttt{params.toml},}

\chapter*{and uncomment the lines below.}

\chapter*{- icon: cv}

\chapter*{icon\_pack: ai}

\chapter*{link: uploads/bfigge\_cv.pdf}

\chapter*{Enter email to display Gravatar (if Gravatar enabled in Config)}

email: "bela.figge@gmail.com"

\chapter*{Highlight the author in author lists? (true/false)}

\section*{highlight\_name: true}

\texttt{$<$br$>$}
I am an applied microeconomist who recently received my PhD in Economics from Georgia State University. I am on the 2025-26 academic job market.

My research examines how decentralized implementation affects policy outcomes. In my job market paper, I estimate that crisis pregnancy centers reduce abortion rates by 18 percent, with effects concentrated among teenagers. 

In published and working papers with coauthors, I study how municipal building codes affect solar energy adoption in Germany and California.

\end{document}
